### 2020-01-07 Literature Review/Literature Review - Revised/sections/MARL.tex
Added Proposal 7.3

>>>>

\section{Learning Dynamics}

Game Dynamics (which I often refer to as Multi Agent Dynamics or Game Dynamics) considers the
problem of mathematically modelling Multi Agent Systems who adapt through repeated interact with one
another. This model then serves to be able to predict the evolution of the system as well as to
understand the trajectory of learning. Typically, this looks at considering whether or not the
method is likely to converge towards a Nash equilibrium. This is generally a difficult problem to
solve \cite{ShohamMultiagentFoundations} for all but toy problems.
\cite{Letcher2019DifferentiableMechanics} shows that the stable equilbrium and Nash equilibrium (NE)
are not necessarily the same and, in fact, argue that stable points are more informative than NEs.
Stability provides some guarantees against the stochastic nature of the environment since a stable
equilibrium will always be returned to even after perturbations. This extremely important in Safe
and Trusted AI as it provides guarantees against undesired behaviour in real world environments.

The area of dynamics which has shown most promise in Multi-Agent Reinforcement Learning is that of
evolutionary dynamics. This draws from the principles of Evolutionary Game Theory (EGT) which
considers similar assumptions to that of MARL: agents are no longer required to be rational and play
the game optimise their expected return through repeated play. Importantly, players have no
knowledge of the others' payoffs \cite{Tuyls2006AnGames}. The first major breakthrough in this field
is in \cite{Borgers1997} where Boergers and Sarin determine the relation between the replicator
dynamics concept of EGT (a differential equation defining the evolution of the proportion of a
subgroup in an evolving population) and the 'Cross' learning method for multi agent reinforcement
learning. This idea is advanced in \cite{Tuyls2006AnGames} where Tuyls et al. determine  a similar
relation for Q-Learning using Boltzmann probabilities as Q-values. The result was a dynamics
equation which describes, for each action, the evolution of its selection probability which could
even account for random exploration. There have since been a number of works which apply the same
insight into different game types and MARL algorithms. In \cite{Bloembergen2015}, these are broken
into the following categories

\begin{itemize}
	\item Stateless games with discrete actions. Here, stateless refers to the idea that the game is
	static and so the environment has no impact on the result. The aforementioned result 
	\cite{Tuyls2006AnGames} fits into this category.
	\item Stateless games with continuous actions. These consider more realistic MARL than the
	previous category by replacing each agent's strategy vector with a probability density function 
	(pdf) over a continuous action space.
	\item Stateful games with discrete actions. This mostly considers stochastic games, where there
	are multiple states with probabilistic (usually Markovian) transitions between them. However,
	extensive form games, which considers more complex phenomena such as sequential moves and
	imperfect information, are also briefly mentioned.
	\item Stateful games with continuous actions. This is one of the more realistic assumptions
	considered. However, the authors point out that this area is yet to see results, leaving it open
	for possible research.
\end{itemize}

Though the above have seen success through experimental validation, most work is applied to bimatrix
games (games of two to three players with finite action spaces). An example of this can be found in
\cite{Hofbauer1996} in which Hofbauer shows that learning a zero-sum bimatrix game follows
Hamiltonian dynamics and results in stable equilibria. Recent work has begun the consideration of
improving the models towards more complex scenarios with larger agent populations. For instance,
Bailey and Piliouras show in \cite{Bailey2019Multi-AgentSystem} that the results of
\cite{Hofbauer1996} can be extended to the n-agent case, even with different network structures.
They show that the result generalises to any zero-sum network game where agents use a
Follow-The-Regularised-Leader learning approach. Another, more recent example of this is 
\cite{Hu2019}, in which Hu uses a mean field approximation to model the dynamics of a population of
Q-Learning agents. As a reminder, mean field (MF) approaches in MARL consider that an agent updates
its strategy based on the mean effect of the population. The result is a system of three equations
which describes the evolution of Q-values over a large population in a symmetric bi-matrix game.This
presents an important first step in modelling the learning dynamics of large agent populations and
has the scope to be expanded to systems of asymmetric games, heterogeneous populations and stateful
n-agent games.

An advantage of determining the evolutionary dynamics of learning is that it can describe the
expected behaviour using different learning methodologies for various game settings. This is
particularly important to understand the convergence of the applied learning method; certain games
will often show cyclic behaviour even with the existence of a strict NE. For instance, Imhof et al.
show in \cite{Imhof2005} that a repeated prisoner's dilemma game results in cyclic behaviour when
considering the options of cooperation or defection. In an interesting twist, Galla shows in
\cite{Galla2011} that this result is dependent on the memory of the agent. Therefore, by using a
method of batch learning, in which agents may discount observations from the distant past, the
agents will move their convergent result from a stict NE (to always defect) to a mixed, stable
equilibrium which promotes cooperation. In \cite{Sanders2018}, Sanders et al. extend this approach
to a general n-player game which is learnt through an experience-weighted attraction method. They
show that the method will display different dynamical behaviour including: convergence to stable
equilibria, limit cycles and chaos. They determine a parameter which describes the likelihood of
complex dynamics and show that, as the number of players increase, the likelihood of complex
dynamics (which will not converge to fixed points) will increase. A similarly interesting result is
that of chaotic dynamics in certain game types and learning algorithms. Sato et al show in
\cite{Sato2002} that Cross learning in two person games result in choatic behaviour and use the
simple rock-paper-scissors game to illustrate this point. In \cite{Foster2001}, Foster and Young
show that in these games, agents cannot learn the future behaviour of their opponents, regardless of
the learning technique. This therefore means that the game does not converge to a NE.

The above discussion highlights just some of the growing body of work regarding the dynamics of
multi-agent learning. It is clear that these studies provide strong insights into the prevalent
problem of multi agent systems, particularly those using reinforcement learning. It allows for an
analysis of the conditions under which learning is possible as well as a method to evaluate
different learning algorithms. However, this field still requires significant work in terms of
generality. A proposal to expand this research is presented in 'Proposed Research'.

### 2020-01-07 Literature Review/Literature Review - Revised/sections/Proposals.tex
Added Proposal 7.3

\section{Stable Exploration in Multi Agent Reinforcement Learning}

This builds on the ideas of \cite{Berkenkamp2017,Jin2018Stability-certifiedPerspective} and an
important point mentioned in \cite{Marinescu2014} that 'the dynamics implied by multi-agent systems
lead to stochastic behaviour resulting sometimes in undesired effects'. In particular, most RL
methods require some trade-off between exploration and exploitation. It is, therefore, required that
we determine a safe manner in which MARL agents may explore without leading to unstable behaviour.
This would require extending the work of \cite{Berkenkamp2017} and/or
\cite{Jin2018Stability-certifiedPerspective} to the multi-agent case. Note that
\cite{Jin2018Stability-certifiedPerspective} does actually consider a multi-agent case, but with
independent learners who do not consider the effect that they have on the other agent(s). The
particular extension that I propose is to consider the coupled effect between agents as part of the
determination of a safe set for exploration.

>>>>

\section{Dynamical Study of Multi Agent Learning}

This builds on the methods and studies presented in 'Learning Dynamics' and an important point
mentioned in \cite{Marinescu2014} that 'the dynamics implied by multi-agent systems lead to
stochastic behaviour resulting sometimes in undesired effects'. It is clear from the discussion that
this study has important implications for MARL. Specifically, it allows us to consider under which
conditions convergence to an equilibrium is possible. It also allows for directed parameter tuning
to ensure that the resultant game yields desired effects. However, this study is still in its
infancy and there are areas yet unexplored. For instance, it would be important to consider the
challenge presented by Bloembergen et al. in \cite{Bloembergen2015} - stateful games with a
continuous action space. This will by no means be trivial and will require strong assumptions
regarding the learning method used and the structure of the game (two-player, symmetric etc). The
analysis presented in \cite{Letcher2019DifferentiableMechanics} regarding Differential Game
Mechanics would prove as a valuable starting point.

Extending to the large n-player case considers the other end of the spectrum which builds on the
work of Hu in \cite{Hu2019} by extending the dynamical study of the mean-field MARL approach which
is gaining popularity. The models may be extended to the consideration of multiple populations,
asymmetric games and continuous action spaces. Perhaps the results presented in \cite{Bellomo2017}
may prove useful in the consideration of the inter-agent effect on the larger population.

Important questions must be considered in this study, such as the ability of agents to predict the
behaviour of other agents. Chaotic dynamics means that this there are limitations to the degree of
predictability that agents show whilst playing a game. These limitations should be explored so that
algorithms which require predictive behaviour may be benchmarked.

As shown in \cite{Bloembergen2015}, these studies are not only useful as a modality for study but
can also be reverse-engineered to develop learning methods which exhibit desired behaviours. To this
end, I propose considering a control theoretic approach towards multi-agent learning. This would
require extending the work of \cite{Berkenkamp2017} and/or
\cite{Jin2018Stability-certifiedPerspective} to the multi-agent case. Note that
\cite{Jin2018Stability-certifiedPerspective} does actually consider a multi-agent case, but with
independent learners who do not consider the effect that they have on the other agent(s). The
particular extension that I propose is to consider the coupled effect between agents using
replicator dynamics.
